\texttt{bayesim}: a tool for fast model fitting with Bayesian inference

### 2018-08-31 paper/Manuscript.tex
working on plotting and paper

 \begin{figure}
   \includegraphics[width=0.7\columnwidth]{figure_1.png}
   \caption{\hl{(Figure copied from docs website for now, will make a publication-appropriate version)}}
   \label{fig1}
 \end{figure}

@@

  \begin{figure}
    \includegraphics[width=0.55\columnwidth]{structure.png}
    \includegraphics[width=0.4\columnwidth]{flowchart.png}
    \caption{Left: \texttt{bayesim} software structure, indicating class definitions, internal and external dependencies, and interfaces. Right: Flowchart of use of \texttt{bayesim}. \hl{(I will update these to make a more sensible figure with less white space, and also add subdivision into the loop)}}
    \label{structure}
  \end{figure}

@@

    \begin{figure}
      \includegraphics[width=0.33\columnwidth]{diode_obs.png}
      \includegraphics[width=0.45\columnwidth]{diode_obs_zoom.png}
%      \includegraphics[width=0.3\columnwidth]{diode_pmf_1.png}
%      \includegraphics[width=0.65\columnwidth]{diode_comp_1.png}
%      \includegraphics[width=0.3\columnwidth]{diode_pmf_2.png}
%      \includegraphics[width=0.65\columnwidth]{diode_comp_2.png}
%      \includegraphics[width=0.3\columnwidth]{diode_pmf_3.png}
%      \includegraphics[width=0.65\columnwidth]{diode_comp_3.png}
%      \caption{a) ``Observations" generated by ideal diode model, Equation~\ref{ID_eqn}, b) Observed data saved by \texttt{bayesim}, with zoom to show where neglected data points were, Next three rows: PMF's, comparisons of highest three probability model points with observed data, and absolute errors thereof, on the initial grid, and after one and two subdivisions, respectively. ``True'' values for the parameters indicated on the PMF in red. (this figure is a giant data dump right now; I'm figuring out how to make it less terrifyingly overwhelming - like possibly overlaying all three PMF's onto one plot in different colors)}
      \includegraphics[width=0.8\columnwidth]{all_PMFs.png}
      \caption{a) ``Observations" generated by ideal diode model, Equation~\ref{ID_eqn}, b) Observed data saved by \texttt{bayesim}, with zoom to show where neglected data points were, c) PMF's after the first inference run, second (one subdivision), and third (two subdivision), in blue, orange, and green, respectively. Values used to generate data indicated in red. \hl{(PMF figure will have a legend and I will add error plots, also observation data could be presented better too)}}
      \label{ID_data}
    \end{figure}

@@

    The lower part of ~\autoref{ID_data} shows the posterior distributions after the first inference run and after each round of subdivision, demonstrating that \texttt{bayesim} gets progressively closer to the ``true" values as the loop continues iterating. In addition, on the first inference run (prior to any subdivision), an average of 46\% of grid points had larger model uncertainty than experimental uncertainty, while after the second subdivision, only 2\% did.

@@

    We start on significantly coarser grid than Ref.~\cite{SnSJoule} and will show one level of subdivision.

>>>>

 \begin{figure}
   \includegraphics[width=0.9\columnwidth]{figure_1.png}
   \caption{\hl{(Figure copied from docs website for now, will make a publication-appropriate version)}}
   \label{fig1}
 \end{figure}

@@

  \begin{figure}
    \includegraphics[width=0.25\columnwidth]{structure.png}
    \includegraphics[width=0.65\columnwidth]{flowchart.png}
    \caption{Left: \texttt{bayesim} software structure. Right: Flowchart of use of \texttt{bayesim}.}
    \label{structure}
  \end{figure}

@@

    \begin{figure}
      \includegraphics[width=0.33\columnwidth]{diode_obs.png}
      \includegraphics[width=0.45\columnwidth]{diode_obs_zoom.png}
%      \includegraphics[width=0.3\columnwidth]{diode_pmf_1.png}
%      \includegraphics[width=0.65\columnwidth]{diode_comp_1.png}
%      \includegraphics[width=0.3\columnwidth]{diode_pmf_2.png}
%      \includegraphics[width=0.65\columnwidth]{diode_comp_2.png}
%      \includegraphics[width=0.3\columnwidth]{diode_pmf_3.png}
%      \includegraphics[width=0.65\columnwidth]{diode_comp_3.png}
%      \caption{a) ``Observations" generated by ideal diode model, Equation~\ref{ID_eqn}, b) Observed data saved by \texttt{bayesim}, with zoom to show where neglected data points were, Next three rows: PMF's, comparisons of highest three probability model points with observed data, and absolute errors thereof, on the initial grid, and after one and two subdivisions, respectively. ``True'' values for the parameters indicated on the PMF in red. (this figure is a giant data dump right now; I'm figuring out how to make it less terrifyingly overwhelming - like possibly overlaying all three PMF's onto one plot in different colors)}
      \includegraphics[width=0.8\columnwidth]{diode_pmf_comp.png}
      \caption{a) ``Observations" generated by ideal diode model, Equation~\ref{ID_eqn}, b) Observed data saved by \texttt{bayesim}, with zoom to show where neglected data points were, c) PMF's after the first inference run, second (one subdivision), and third (two subdivision), in blue, orange, and green, respectively. Values used to generate data indicated in red.}
      \label{ID_data}
    \end{figure}

@@

    The lower part of ~\autoref{ID_data} shows the posterior distributions after the first inference run and after each round of subdivision, demonstrating that \texttt{bayesim} gets progressively closer to the ``true" values as the loop continues iterating. In addition, on the first inference run (prior to any subdivision), an average of 43\% of grid points had larger model uncertainty than experimental uncertainty, while after the second subdivision, only 2\% did, while the average absolute error of the highest-probability model decreased from 0.03 after the first run to 0.007 after the second subdivision.

@@

    \begin{figure}
      \includegraphics[width=0.7\columnwidth]{SnS_final_pmf.png}
      \includegraphics[width=0.8\columnwidth]{SnS_probs_Joule}
      \caption{Above: PMF produced by \texttt{bayesim}. Below: PMF from Reference~\cite{SnSJoule}. \hl{TBD if we'll actually reproduce the plot from the Joule paper directly vs. replotting the data somehow}}
      \label{SnS_data}
    \end{figure}

    We start on a significantly coarser grid than Ref.~\cite{SnSJoule} and show only one level of subdivision to make the example feasible to run on a personal computer. \~autoref{SnS_data} shows the results from this fit done in \texttt{bayesim} compared to the higher-resolution grid analysis done previously. Note that the inference step in full-resolution grid took a few hours, while the adaptive grid fit takes a few minutes. While the fit precision is of course lower at only one level of subdivision, the extracted values are generally in agreement and more importantly, the relationship between the mobility and lifetime (namely, that the product, i.e. the diffusion length), is constrained, emerges just as clearly.
